\documentclass[12pt, letterpaper]{article}

\usepackage[margin=1in, headheight=14pt]{geometry}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{tocloft}

\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue,
    pdftitle={Project Breakdown -- 2D Platformer}}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small Project Breakdown}
\fancyhead[R]{\small 2D Platformer Game}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\begin{document}

% ── Cover ─────────────────────────────────────────────────────────────────────
\begin{titlepage}
    \centering
    \vspace*{3cm}
    {\Huge\bfseries Project Breakdown\par}
    \vspace{0.4cm}
    \rule{\linewidth}{0.5pt}
    \vspace{0.4cm}
    {\LARGE 2D Platformer Game\par}
    \vspace{0.3cm}
    {\large Components, Tools, and Dependency Manifest\par}
    \vspace{2cm}
    \begin{tabular}{rl}
        \textbf{Version:} & 1.0 \\[4pt]
        \textbf{Date:}    & \today \\[4pt]
        \textbf{Authors:} & Development Team \\
    \end{tabular}
    \vfill
    \rule{\linewidth}{0.5pt}
\end{titlepage}

\newpage
\tableofcontents
\newpage

% ── 1. Overview ───────────────────────────────────────────────────────────────
\section{Project Overview}

A 2D sprite-based platformer with three containerized services: a Pygame game client, a FastAPI leaderboard backend, and a PostgreSQL database. Services communicate over a shared Docker bridge network.

% ── 2. Screens ────────────────────────────────────────────────────────────────
\section{Game Screens}

\begin{longtable}{p{3.5cm} p{9.5cm}}
    \toprule
    \textbf{Screen} & \textbf{Description} \\
    \midrule
    \endfirsthead
    \toprule
    \textbf{Screen} & \textbf{Description} \\
    \midrule
    \endhead
    \bottomrule
    \endfoot
    Main Menu      & Title, Start, Leaderboard, and Quit buttons. Background music. \\
    \addlinespace
    Level Select   & Grid of levels. Lock/unlock state read from local save file. \\
    \addlinespace
    Gameplay       & Core loop: player movement, physics, collision, enemies, HUD, collectibles. \\
    \addlinespace
    Pause Menu     & Overlay on gameplay. Resume, Restart, Main Menu. \\
    \addlinespace
    Game Over      & Displays score. Retry or return to Main Menu. \\
    \addlinespace
    Victory        & Score summary. Submits result to leaderboard API. \\
    \addlinespace
    Leaderboard    & Fetches and displays top scores from the backend. \\
\end{longtable}

% ── 3. API ────────────────────────────────────────────────────────────────────
\section{Leaderboard API}

FastAPI service with four endpoints:

\begin{longtable}{p{4cm} p{1.8cm} p{7.2cm}}
    \toprule
    \textbf{Route} & \textbf{Method} & \textbf{Description} \\
    \midrule
    \endfirsthead
    \toprule
    \textbf{Route} & \textbf{Method} & \textbf{Description} \\
    \midrule
    \endhead
    \bottomrule
    \endfoot
    \texttt{/health}         & GET    & Service health check. \\
    \texttt{/scores}         & GET    & Returns top N scores ordered by score descending. \\
    \texttt{/scores}         & POST   & Accepts player name and score; writes to database. \\
    \texttt{/scores/\{id\}}  & DELETE & Removes a score record by ID. \\
\end{longtable}

% ── 4. Dependencies ───────────────────────────────────────────────────────────
\section{Dependency Manifest}

\subsection{Game Client --- \texttt{python:3.12-slim}}

\begin{longtable}{p{4.5cm} p{2cm} p{7cm}}
    \toprule
    \textbf{Package} & \textbf{Type} & \textbf{Purpose} \\
    \midrule
    \endfirsthead
    \toprule
    \textbf{Package} & \textbf{Type} & \textbf{Purpose} \\
    \midrule
    \endhead
    \bottomrule
    \endfoot
    \texttt{pygame}            & Python & Rendering, input, audio, sprites \\
    \texttt{requests}          & Python & HTTP calls to the leaderboard API \\
    \texttt{pytmx}             & Python & Tiled \texttt{.tmx} map file loading \\
    \texttt{python-dotenv}     & Python & Environment variable loading \\
    \texttt{libsdl2-dev}       & System & SDL2 core (window, input) \\
    \texttt{libsdl2-image-dev} & System & Sprite/image loading \\
    \texttt{libsdl2-mixer-dev} & System & Audio playback \\
    \texttt{libsdl2-ttf-dev}   & System & Font rendering \\
    \texttt{libx11-dev}        & System & Display output (X11) \\
\end{longtable}

\subsection{Leaderboard API --- \texttt{python:3.12-slim}}

\begin{longtable}{p{4.5cm} p{2cm} p{7cm}}
    \toprule
    \textbf{Package} & \textbf{Type} & \textbf{Purpose} \\
    \midrule
    \endfirsthead
    \toprule
    \textbf{Package} & \textbf{Type} & \textbf{Purpose} \\
    \midrule
    \endhead
    \bottomrule
    \endfoot
    \texttt{fastapi}           & Python & Web framework and routing \\
    \texttt{uvicorn[standard]} & Python & ASGI server \\
    \texttt{sqlalchemy}        & Python & ORM / database layer \\
    \texttt{psycopg2-binary}   & Python & PostgreSQL driver \\
    \texttt{pydantic}          & Python & Request and response validation \\
    \texttt{python-dotenv}     & Python & Environment variable loading \\
\end{longtable}

\subsection{Database --- \texttt{postgres:16-alpine}}

Official PostgreSQL image. No custom Dockerfile required. Schema seeded via \texttt{db/init.sql} mounted to \texttt{/docker-entrypoint-initdb.d/}. Data persisted to a named Docker volume.

\end{document}
