\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}

\title{CS3338 Final Project: Snapshot Objectives}
\author{Group 6}
\date{May 2026}

\begin{document}

\maketitle

\section{Snapshot 1: Base Core Framework}
The primary objective of this snapshot was to establish the development environment and the fundamental physics of the 2D platformer.
\begin{itemize}
    \item Configure Docker-Compose environment for containerized development.
    \item Implement basic character physics including horizontal movement and gravity-based jumping.
    \item Create the main menu shell and basic screen transitions.
    \item Establish a sprite asset pipeline for character and environment tiles.
\end{itemize}

\section{Snapshot 2: Abilities and Combat Mechanics}
This milestone focused on the first "large feature" addition: the player's interaction with the game world through abilities.
\begin{itemize}
    \item Develop weapon projectile logic and collision hitboxes.
    \item Integrate ability-specific character sprites and animation synchronization.
    \item Implement initial HUD elements for tracking player status.
    \item Conduct weapon execution testing via TestRail.
\end{itemize}

\section{Snapshot 3: World Interaction and AI}
The third snapshot expanded the game logic to include objective-based gameplay and reactive elements.
\begin{itemize}
    \item Implement "Victory Trigger" logic for reaching the end-of-level goal.
    \item Develop Enemy AI patrol patterns and player detection scripts.
    \item Refine HUD accuracy for scoring and level progress.
    \item Identify "Areas of Weakness" through failed test cases (e.g., Enemy AI collision).
\end{itemize}

\section{Snapshot 4: Final Polish and Future Work}
The final milestone focuses on stability, optimization, and planning for the project's next phase.
\begin{itemize}
    \item Perform stress testing for FPS stability across different OS platforms.
    \item Conduct final code review and refactor for Docker deployment.
    \item Document "Future Work" objectives including Local Multiplayer Support.
    \item Complete the full TestRail summary reporting for final submission.
\end{itemize}

\end{document}